Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-06 ms.tex
still writing goodness-of-fit section

The posterior sampling framework thus far described also affords us an
opportunity to evaluate the goodness-of-fit for competing dust SED models, and 
thereby cross-check the conclusions of our correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for each pixel, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$
% maybe invent a term chi^2_p or something to 
% reduce potential confusion caused by notation

@@

% mention that when t floats, we find a lower T than the Planck team?
% mention beta template but floating t, normalization

Next, we calculate $\chi^2_{\nu}$ for the two-component model with global 
parameters from FDS99 (Table \ref{tab:global}, model 2). We find 
$\chi^2_{\nu}$=2.33, a slight improvement relative to the $\beta$=1.59 
single-MBB model. Finally, calculate $\chi^2_{\nu}$ for Table \ref{tab:global} 
model 3, the two-component model favored by our \PLANCK+DIRBE correlation 
slopes. In this case, we achieve the best goodness-of-fit out of the all the 
models tested, with $\chi^2_{\nu}$=2.11.

@@

% could compare temperatures, but masks are different

>>>>

The posterior sampling framework thus far described also affords us an
opportunity to evaluate the goodness-of-fit for competing dust SED models, and 
thereby cross-check the conclusions of our correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for each pixel, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$.
% maybe invent a term chi^2_p or something to 
% reduce potential confusion caused by notation

@@

% mention that when t floats, we find a lower T by ~ 1 degree than the Planck 
%team?

We move on to evaluate two-component models, first calculating $\chi^2_{\nu}$ 
with the FDS99 global parameters (Table \ref{tab:global}, model 2). We find
$\chi^2_{\nu}$=2.33, a slight improvement relative to the best-fitting
single-MBB models. Finally, calculate $\chi^2_{\nu}$ for Table 
\ref{tab:global} model 3, the two-component model favored by our \PLANCK+DIRBE 
correlation slopes. In this case, we achieve the best goodness-of-fit out of 
all the models we have tested, with $\chi^2_{\nu}$=2.11.

Thus, our degree-resolution goodness-of-fit analysis has generally confirmed
the conclusions of $\S$\ref{sec:global}. We find the single-MBB $\beta$ value 
favored by the combination of \PLANCK~and DIRBE to be nearly identical here 
($\beta$=1.57) versus in $\S$\ref{sec:global}. As in $\S$\ref{sec:global}, we 
also find that the \PLANCK+FIRAS and\PLANCK+DIRBE best-fit two-component models
from Table \ref{tab:global} outperform single-MBB alternatives, though only by 
a relatively small margin. The agreement between our correlation slope analysis
and the present goodness-of-fit analysis is especially encouraging for two main
reasons: (1) in the present analysis, dust temperature was allowed to vary on 
degree scales, whereas in $\S$\ref{sec:global} we assumed a single global dust 
temperature (2)

@@

% could compare temperatures from correlation slope analysis versus here, but 
% masks are different, so i guess it's just not worth it
